Machine-learned embedded atom method

### 2019-10-22 doc/papers/ml-eam/manuscript.tex
Fix some errors in the manuscript.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: Mo - EOS
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}
\centering
\includegraphics[scale=0.65]{figures/Mo_all_eos.png}
\caption{\label{fig:Mo_eos} The energy-volume curves of the original EAM, 
ML-EAM and DFT for the fcc Ni.}
\end{figure}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Mo - Material Properties
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}
\centering
\begin{tabular}{lcccccc}
\hline
                              & DFT  & SNAP \cite{SNAP_Mo} & EAM \cite{ZJW2} & ML-EAM         & ML-ADP         & Exp.                      \\
\hline
$T_{m}$(K)                    &      & 3000                & 3750            & 2940           & 2880           & 2890                      \\
$c_{11}$ (GPa)                & 472  & 473 (0.2\%)         & 457 (-3.2\%)    & 472 (0.0\%)    & 473 (0.2\%)    & 479 \cite{Mo_Elastic_Exp} \\
$c_{12}$ (GPa)                & 158  & 152 (-3.8\%)        & 168 (6.3\%)     & 158 (0.0\%)    & 160 (1.2\%)    & 165 \cite{Mo_Elastic_Exp} \\
$c_{44}$ (GPa)                & 106  & 107 (0.9\%)         & 116 (9.4\%)     & 106 (0.0\%)    & 105 (-0.9\%)   & 108 \cite{Mo_Elastic_Exp} \\
$B_{\mathrm{VRH}}$ (GPa)      & 263  & 259 (-1.5\%)        & 264 (0.4\%)     & 262 (-0.4\%)   & 264 (0.4\%)    & 270 \cite{Mo_Elastic_Exp} \\
$G_{\mathrm{VRH}}$ (GPa)      & 124  & 126 (1.6\%)         & 127 (2.4\%)     & 125 (0.8\%)    & 124 (0.0\%)    & 125 \cite{Mo_Elastic_Exp} \\
$\mu$                         & 0.30 & 0.29 (-3.3\%)       & 0.29 (-3.3\%)   & 0.30 (0.9\%)   & 0.30 (0.0\%)   & 0.30                      \\
$E_{v}$ (eV)                  & 2.87 & 2.61 (-9.1\%)       & 3.02 (5.2\%)    & 1.16 (-20.5\%) & 1.71 (17.1\%)  &                           \\
$E_{m}$ (eV)                  & 1.12 & 1.39 (24.1\%)       & 1.54 (37.5\%)   & 1.46 (30.5\%)  & 0.87 (-22.3\%) &                           \\
$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%)       & 4.56 (14.3\%)   & 2.62 (1.6\%)   & 2.58 (0.0\%)   & 4.00 \cite{Mo_Ea_Exp}     \\
\hline
\end{tabular}
\caption{\label{table:Mo_properties} Comparison of the calculated and 
experimental material properties of elementary bcc Mo. SNAP refers to the 
elementary Mo SNAP model.
}
\end{table*}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: Alloy EOS - Plot
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure*}
\centering
\includegraphics[scale=0.5]{figures/alloy_eos.png}
\caption{\label{fig:alloy_eos} $\rho(r)$, $F(\rho)$, $\phi(r)$ of the original 
Zjw04 EAM, ML-EAM and ML-ADP. \textbf{(d)} shows the $\mu(r)$ and $\omega(r)$ of 
ML-ADP.}
\end{figure*}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Mo-Ni MAE
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}
\centering
\begin{tabular}{lcccccccc}
\hline
                  & Model            & Mo   & Ni$_4$Mo & Ni$_3$Mo & Mo$_{\mathrm{Ni}}$ & Ni$_{\mathrm{Mo}}$ & Ni   & Overall \\
\hline
Energy (meV/atom) & SNAP \cite{SNAP} & 16.2 & 4.0      & 5.2      & 22.7               & 33.9               & 7.9  & 22.5    \\
                  & ML-EAM           & 30.4 & 11.1     & 8.6      & 29.8               & 33.9               & 11.6 & 26.2    \\
                  & ML-ADP           & 36.9 & 5.1      & 4.8      & 21.7               & 22.8               & 13.3 & 19.6    \\
\hline
Force (eV/\AA)    & SNAP \cite{SNAP} & 0.29 & 0.14     & 0.16     & 0.13               & 0.55               & 0.11 & 0.23    \\
                  & ML-EAM           & 0.33 & 0.24     & 0.19     & 0.25               & 0.35               & 0.08 & 0.23    \\
                  & ML-ADP           & 0.45 & 0.16     & 0.15     & 0.14               & 0.35               & 0.08 & 0.20    \\
\hline
\end{tabular}
\caption{\label{table:MAE}
Comparion of the MAEs in predicted energies (mev/atom) and forces (eV/\AA) 
relative to the DFT on the entire Mo-Ni dataset.}
\end{table*}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Mo-Ni Elastic Constants
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}
\centering
\begin{tabular}{lccccc}
\hline
                   & DFT  & SNAP \cite{SNAP} & EAM \cite{ZJW2} & ML-EAM        & ML-ADP        \\
\hline
Ni$_3$Mo \\
$c_{11}$           & 385  & 420 (9.1\%)      & 195 (-49.4\%)   & 403 (4.7\%)   & 374 (-2.9\%)  \\
$c_{12}$           & 166  & 197 (18.7\%)     & 98 (-41.0\%)    & 208 (25.3\%)  & 160 (-3.6\%)  \\
$c_{13}$           & 145  & 162 (11.7\%)     & 98 (-32.4\%)    & 230 (58.6\%)  & 176 (21.4\%)  \\
$c_{22}$           & 402  & 360 (10.7\%)     & 351 (-12.7\%)   & 443 (10.2\%)  & 386 (-4.0\%)  \\
$c_{23}$           & 131  & 145 (-10.4\%)    & 107 (-18.3\%)   & 272 (107.6\%) & 214 (63.3\%)  \\
$c_{33}$           & 402  & 408 (1.5\%)      & 295 (-26.6\%)   & 474 (17.9\%)  & 398 (-0.5\%)  \\
$c_{44}$           & 94   & 84 (-10.4\%)     & 36 (-61.7\%)    & 25 (-73.4\%)  & 52 (-44.6\%)  \\
$B_{\mathrm{VRH}}$ & 230  & 243 (5.7\%)      & 156 (-32.2\%)   & 302 (31.3\%)  & 250 (8.7\%)   \\
$G_{\mathrm{VRH}}$ & 89   & 100 (12.4\%)     & 61 (-31.5\%)    & 57 (36.0\%)   & 66 (25.8\%)   \\
$\mu$              & 0.33 & 0.32 (-3.0\%)    & 0.33 (0.0\%)    & 0.41 (24.2\%) & 0.38 (15.1\%) \\
\hline
Ni$_4$Mo \\
$c_{11}$           & 300  & 283 (-5.7\%)     & 172 (-42.7\%)   & 282 (-6.0\%)  & 342 (14.0\%)  \\
$c_{12}$           & 186  & 179 (-3.8\%)     & 158 (-15.1\%)   & 125 (-32.8\%) & 217 (16.7\%)  \\
$c_{22}$           & 313  & 326 (4.2\%)      & 158 (-49.5\%)   & 282 (-10.0\%) & 342 (9.3\%)   \\
$c_{23}$           & 166  & 164 (-1.2\%)     & 80 (-51.8\%)    & 156 (-6.0\%)  & 232 (39.8\%)  \\
$c_{44}$           & 130  & 126 (-3.1\%)     & 125 (-3.8\%)    & 136 (4.6\%)   & 117 (-10.0\%) \\
$B_{\mathrm{VRH}}$ & 223  & 220 (-1.3\%)     & 161 (-27.8\%)   & 178 (-20.1\%) & 257 (15.2\%)  \\
$G_{\mathrm{VRH}}$ & 91   & 95 (4.4\%)       & -156 (-162\%)   & 80 (-12.1\%)  & 79 (-13.2\%)  \\
$\mu$              & 0.33 & 0.31 (-6.1\%)    & 0.70 (112\%)    & 0.31 (-6.1\%) & 0.36 (9.1\%)  \\
\hline
\end{tabular}
\caption{\label{table:NiMo_elastic_constants}
Comparion of elastic constants ($c_{ij}$, GPa), Voigt-Reuss-Hill bulk modulus 
($B_{\mathrm{VRH}}$, GPa), Voigt-Reuss-Hill shear modulus ($G_{\mathrm{VRH}}$, 
GPa) and homogeneous Poisson's ratio ($\mu$) for fcc Ni, fcc Mo and binary 
alloys Ni$_{3}$Mo and Ni$_{4}$Mo.
}
\end{table*}

>>>>

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: Mo - EOS
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure}
\centering
\includegraphics[scale=0.65]{figures/Mo_all_eos.png}
\caption{\label{fig:Mo_eos} The energy-volume curves of the original EAM, 
ML-EAM and DFT for the bcc Mo.}
\end{figure}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Mo - Material Properties
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}
\centering
\begin{tabular}{lcccccc}
\hline
                              & DFT  & SNAP \cite{SNAP_Mo} & EAM \cite{ZJW2} & ML-EAM         & ML-ADP         & Exp.                      \\
\hline
$T_{m}$(K)                    &      & 3000                & 3750            & 2940           & 2880           & 2890                      \\
$c_{11}$ (GPa)                & 472  & 473 (0.2\%)         & 457 (-3.2\%)    & 472 (0.0\%)    & 473 (0.2\%)    & 479 \cite{Mo_Elastic_Exp} \\
$c_{12}$ (GPa)                & 158  & 152 (-3.8\%)        & 168 (6.3\%)     & 158 (0.0\%)    & 160 (1.2\%)    & 165 \cite{Mo_Elastic_Exp} \\
$c_{44}$ (GPa)                & 106  & 107 (0.9\%)         & 116 (9.4\%)     & 106 (0.0\%)    & 105 (-0.9\%)   & 108 \cite{Mo_Elastic_Exp} \\
$B_{\mathrm{VRH}}$ (GPa)      & 263  & 259 (-1.5\%)        & 264 (0.4\%)     & 262 (-0.4\%)   & 264 (0.4\%)    & 270 \cite{Mo_Elastic_Exp} \\
$G_{\mathrm{VRH}}$ (GPa)      & 124  & 126 (1.6\%)         & 127 (2.4\%)     & 125 (0.8\%)    & 124 (0.0\%)    & 125 \cite{Mo_Elastic_Exp} \\
$\mu$                         & 0.30 & 0.29 (-3.3\%)       & 0.29 (-3.3\%)   & 0.30 (0.9\%)   & 0.30 (0.0\%)   & 0.30                      \\
$E_{v}$ (eV)                  & 2.87 & 2.61 (-9.1\%)       & 3.02 (5.2\%)    & 1.99 (-30.7\%) & 2.01 (-30.0\%) &                           \\
$E_{m}$ (eV)                  & 1.12 & 1.39 (24.1\%)       & 1.54 (37.5\%)   & 1.33 (18.7\%)  & 1.27 (13.4\%)  &                           \\
$E_{a} = E_{v} + E_{m} $ (eV) & 3.99 & 4.00 (-0.1\%)       & 4.56 (14.3\%)   & 3.32 (-16.8\%) & 3.28 (-17.8\%) & 4.00 \cite{Mo_Ea_Exp}     \\
\hline
\end{tabular}
\caption{\label{table:Mo_properties} Comparison of the calculated and 
experimental material properties of elementary bcc Mo. SNAP refers to the 
elementary SNAP Mo model.
}
\end{table*}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Figure: Alloy EOS - Plot
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{figure*}
\centering
\includegraphics[scale=0.5]{figures/alloy_eos.png}
\caption{\label{fig:alloy_eos} Energy-volume curves of Ni$_3$Mo and Ni$_4$Mo 
obtained with the original Zjw04 EAM, ML-EAM, ML-ADP and DFT.}
\end{figure*}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Mo-Ni MAE
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}
\centering
\begin{tabular}{lcccccccc}
\hline
                  & Model            & Mo   & Ni$_4$Mo & Ni$_3$Mo & Mo$_{\mathrm{Ni}}$ & Ni$_{\mathrm{Mo}}$ & Ni   & Overall \\
\hline
Energy (meV/atom) & SNAP \cite{SNAP} & 16.2 & 4.0      & 5.2      & 22.7               & 33.9               & 7.9  & 22.5    \\
                  & ML-EAM           & 30.4 & 11.1     & 8.6      & 29.8               & 33.9               & 11.6 & 26.2    \\
                  & ML-ADP           & 36.9 & 5.1      & 4.8      & 21.7               & 22.8               & 13.3 & 19.6    \\
\hline
Force (eV/\AA)    & SNAP \cite{SNAP} & 0.29 & 0.14     & 0.16     & 0.13               & 0.55               & 0.11 & 0.23    \\
                  & ML-EAM           & 0.33 & 0.24     & 0.19     & 0.25               & 0.35               & 0.08 & 0.23    \\
                  & ML-ADP           & 0.45 & 0.16     & 0.15     & 0.14               & 0.35               & 0.08 & 0.20    \\
\hline
\end{tabular}
\caption{\label{table:MAE}
Comparion of the MAEs in predicted energies (mev/atom) and forces (eV/\AA) 
relative to the DFT on the subsets (Mo, Ni$_4$Mo, Ni$_3$Mo, Ni-doped Mo, 
Mo-doped Ni, Ni) and the entire Mo-Ni dataset.}
\end{table*}

@@

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Table: Mo-Ni Elastic Constants
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{table*}
\centering
\begin{tabular}{lccccc}
\hline
                   & DFT  & SNAP \cite{SNAP} & EAM \cite{ZJW2} & ML-EAM        & ML-ADP        \\
\hline
Ni$_3$Mo \\
$c_{11}$           & 385  & 420 (9.1\%)      & 195 (-49.4\%)   & 403 (4.7\%)   & 374 (-2.9\%)  \\
$c_{12}$           & 166  & 197 (18.7\%)     & 98 (-41.0\%)    & 208 (25.3\%)  & 160 (-3.6\%)  \\
$c_{13}$           & 145  & 162 (11.7\%)     & 98 (-32.4\%)    & 230 (58.6\%)  & 176 (21.4\%)  \\
$c_{22}$           & 402  & 360 (10.7\%)     & 351 (-12.7\%)   & 443 (10.2\%)  & 386 (-4.0\%)  \\
$c_{23}$           & 131  & 145 (-10.4\%)    & 107 (-18.3\%)   & 272 (107.6\%) & 214 (63.3\%)  \\
$c_{33}$           & 402  & 408 (1.5\%)      & 295 (-26.6\%)   & 474 (17.9\%)  & 398 (-0.5\%)  \\
$c_{44}$           & 94   & 84 (-10.4\%)     & 36 (-61.7\%)    & 25 (-73.4\%)  & 52 (-44.6\%)  \\
$B_{\mathrm{VRH}}$ & 230  & 243 (5.7\%)      & 156 (-32.2\%)   & 302 (31.3\%)  & 250 (8.7\%)   \\
$G_{\mathrm{VRH}}$ & 89   & 100 (12.4\%)     & 61 (-31.5\%)    & 57 (36.0\%)   & 66 (25.8\%)   \\
$\mu$              & 0.33 & 0.32 (-3.0\%)    & 0.33 (0.0\%)    & 0.41 (24.2\%) & 0.38 (15.1\%) \\
\hline
Ni$_4$Mo \\
$c_{11}$           & 300  & 283 (-5.7\%)     & 172 (-42.7\%)   & 282 (-6.0\%)  & 342 (14.0\%)  \\
$c_{12}$           & 186  & 179 (-3.8\%)     & 158 (-15.1\%)   & 125 (-32.8\%) & 217 (16.7\%)  \\
$c_{22}$           & 313  & 326 (4.2\%)      & 158 (-49.5\%)   & 282 (-10.0\%) & 342 (9.3\%)   \\
$c_{23}$           & 166  & 164 (-1.2\%)     & 80 (-51.8\%)    & 156 (-6.0\%)  & 232 (39.8\%)  \\
$c_{44}$           & 130  & 126 (-3.1\%)     & 125 (-3.8\%)    & 136 (4.6\%)   & 117 (-10.0\%) \\
$B_{\mathrm{VRH}}$ & 223  & 220 (-1.3\%)     & 161 (-27.8\%)   & 178 (-20.1\%) & 257 (15.2\%)  \\
$G_{\mathrm{VRH}}$ & 91   & 95 (4.4\%)       & -156 (-162\%)   & 80 (-12.1\%)  & 79 (-13.2\%)  \\
$\mu$              & 0.33 & 0.31 (-6.1\%)    & 0.70 (112\%)    & 0.31 (-6.1\%) & 0.36 (9.1\%)  \\
\hline
\end{tabular}
\caption{\label{table:NiMo_elastic_constants}
Comparion of elastic constants ($c_{ij}$, GPa), Voigt-Reuss-Hill bulk modulus 
($B_{\mathrm{VRH}}$, GPa), Voigt-Reuss-Hill shear modulus ($G_{\mathrm{VRH}}$, 
GPa) and homogeneous Poisson's ratio ($\mu$) for fcc Ni, bcc Mo and binary 
alloys Ni$_{3}$Mo and Ni$_{4}$Mo.
}
\end{table*}
